%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

\vspace*{-.2cm}
\section{Design Discussion}
\label{sec:design_discussion}

%The top-down and bottom-up designs introduced in the previous section have 
%their own pros and cons. 
% to extend OpenStack with multi-site collaboration.
In this section, we discuss the pros and cons of the \emph{top-down} and
\emph{bottom-up} designs targeted at the end of the previous section.
More precisely, our discussion is driven by the following questions. (i) On the
one hand, while the top-down design is the most common approach, can it fulfill
all the expected requirements listed in our classification without requiring
changes in the VIM codebase? (ii) On the other hand, while the bottom-up design
seems to disrupt the design principles by requiring \emph{a la peer-to-peer}
strategies in VIM's internal mechanisms, should it be discarded?

\paragraph{Top-Down Design}
The top-down approach consists in designing a set of overlay
components that interact with existing VIM APIs to avoid modifying VIM
codebases.
%
Avoiding codebase modifications is of particular importance in
fast-growing software stacks. For example, a new version of OpenStack
is released every six months with a lot of changes in the codebase,
whereas changes rarely impact the APIs.
%
Therefore, a top-down design makes VIM development and the overlay
system components independent. If designed to do so, the system can
easily allow L4, \ie the support of different versions
and types of VIMs - as demonstrated by
FogBow~\cite{brasileiro2016fogbow}.

Unfortunately, a top-down design cannot satisfy all L2 requirements
without extending or revising the existing VIM codebase. For example,
OpenStack Tricircle~\cite{tricircle}, a top-down project to allow
virtual networking across different sites, ended up "breaking" the
core of OpenStack by introducing specific L2 mechanisms. Such
intrusive modifications negate the aforementioned independence.
%
Moreover, L2 features in general require reimplementing 
many low-level VIM functionalities at the overlay level. For
instance, the OpenStack ``boot a VM'' process looks as follows from a
bird's-eye view: (1) Get the URL of the image by looking up in the
database, (2) Schedule and boot the VM. Thus, booting a VM on
\emph{Site 1} using an image defined in \emph{Site 2} would require
implementing a dedicated workflow at the overlay level in order to
interact with both sites and copy the image from the image manager
(\ie Glance) of \emph{Site 2} to the one of \emph{Site 1} before booting the VM. 
%
This is valid for most L2 features such as a fine-grained
authorization management with different rights in different \edge
sites (L2.1) or a cross-site scheduling functionality when sites are
specified implicitly (L2.2). Such a mechanism will be similar to the
placement workflow already available in \texttt{Nova}.

%
%%FW: I do not like the example above, it already assumes a specific solution, I suggest we use the following
%For instance, when sites are specified implicitly (cf. L2.2) a scheduling functionality 
%needs to be implemented at the overlay-level, similar to the scheduling functionality
%already in \texttt{nova}.  
%This is in fact the case for most L2 features such as a fined authorization management
%with different rights in different Edge sites.
%% Also, I do not know if the following is a pro or a con
%Finally, we should also keep in mind that the L3 requirements related
%to network split-brains imply to design the overlay components \emph{a
%  la peer-to-peer}, which might increase the complexity of this
%approach.



%------Moreover, if different VIM flavors are deployed, it might become impractical to provide a single VIM management-view to users as different VIMs might have specific features that need to be managed.


\paragraph{Bottom-Up Design}
In a bottom-up design, the system is not limited by what is available through VIM APIs. 
Specifically, there are two possibilities: i) rearchitecting  the services/components of existing cloud platforms, in our case OpenStack; ii) through a clean-slate approach.

%Specifically 
By rearchitecting OpenStack to allow native
collaboration, several `local' features can be supported across the entire
\edge infrastructure for free. For instance, the aforementioned
OpenStack ``boot a VM on Site 1 with image on Site 2'' process would
be feasible without modifying the VIM codebase if \emph{Site 1} can
either directly contact the image manager of \emph{Site 2}, or share
the database backend with \emph{Site 2}.
%However, the efficiency and ease of use brought by native collaboration come at a cost. 
However, since OpenStack has not been designed to be collaborative, most
mechanisms must be revised to consider side-effects related to
collaboration operations.
%, like one of the edge scenarios, in mind.
%
For instance, a VM boot process initiated on \emph{Site 1} can be
completed on \emph{Site 2}. The question is then to define where the states
related to this VM should be stored, keeping in mind the split-brain
challenge.
%
It is noteworthy that identifying all these aspects requires the understanding of
existing code, which is a daunting task in respect to the OpenStack
ecosystem size.
% 

Therefore, the complexity of rearchitecting existing services/components might make a clean-slate approach as the most likely approach for a bottom-up design.

Finally, L4 requirements cannot be intrinsically satisfied by the
bottom-up approach while L5 implies strong limitations regarding how
collaborations should be implemented (for instance sharing internal
states of different \edge sites between operators looks unlikely).

% This kind of collaboration may be achieved with a collaborative
% backend that relies on a notion of \emph{space}. \emph{Space} says in
% which space the OpenStack lookup and write data. It could be an Edge
% site or a combination of Edge sites if the collaboration is needed. It
% leads to a more efficient system, one without the need to repeatedly
% implement features at different levels.  However, implementing a
% backend based on a notion of space represents a scientific challenge.
%

% With the high industry demand
% for a working Edge system, this means that modifying or extending
% OpenStack is in most cases too expensive (time and resource wise).
% Note also that such backend will not free the developer to implement
% specific workflows for intra-services scenarios\RACm{For instance the
%   ``list of actually scheduling VM'' could not be reused from vanilla
%   code}.


\paragraph{Summary}
There are \emph{pros} and \emph{cons} for both approaches,
and none individually seems to meet all requirements.
From the technical perspective, the bottom-up
design seems to be the most appropriate to cope with L1, L2 and L3
requirements, while the top-down is the only one to satisfy L4
and L5.
%
From the business perspective, a top-down approach is likely to fulfill the
short and medium-term Time-To-Market (TTM) requirements while a bottom-up
approach is required to fulfill all requirements. 
%
From the codebase perspective, top-down approach has limited impact on 
existing VIM codebase while the bottom-up, despite the impact 
on existing codebase, allows implementing functionalities efficiently, without code
duplication. 
%
All in all, our community should investigate a long-term solution that
builds on a bottom-up approach.  This will require first diving into
OpenStack and understanding its intricate internal mechanisms leveraging
tools like EnOS~\cite{cherrueau2017toward} to mitigate the efforts,
and second, to address scientific challenges such as the definition of
a reference architecture for a resource management system for \edge
infrastructures, how to share internal system states in an \edge
context etc. 







%%As a starting point, early \emph{bottom-up} efforts
%% \JM{Ronan, reference to your paper?}
%%  can be taken into account along with mechanisms that have been implemented in \emph{top-down} solutions but can be applied in a \emph{bottom-up} way~\cite{ericsson-p2p}.


%% \JM{Would a picture somewhere in the paper with a simplified view of a top-down system vs a bottom-up one help the reader? Maybe in section 3.3? I think it would be useful, but we would need to cut somewhere to make it fit in the 5 pages}

%NOTES:
%The way to go is bottom up. Top-down, fastest TTM, a quick fix. That is how everyone is doing it, and thatis the way. BUt that is no the way it should be designed. Short-medium term, top-down...long-run, bottom-up.
%Refer to:
%http://ieeexplore.ieee.org/abstract/document/1334777/
%Top-down: requirements, then implement it
%Bottom-up: not all requirments, but implement something. Can top-down approaches be partially used and implemented in a bottom-up.

