
\section{Introduction}
\label{sec:intro}


% Edge Infrastructures are the next platform
With the emergence of Internet of Things applications (IoT) and new
usages related Network Function
Virtualization technologies (NFV), Cloud and Network communities are now advocating
for going towards massively distributed small sized infrastructures
that are deployed at the edge of the network.
%
Referred to as the Edge Computing paradigm, this model has been attracting
growing interest for the last few years as it enables delivering Cloud
Computing capabilities closer to end-users, their related devices, and the applications.
%

%% A lot of academics works focus on how to leverage these
%% infrastructures to address specicifc use-cases
While several academic studies have highlighed the advantages of Edge
Computing infrastructures in various
domains~\cite{bonomi2012fog,zhang2015cloud,7574435,satyanarayanan2017emergence},
the development of
%%  We need a resource management system that enables administrators to
%% operate and end-users to use edge resources.
a resource management system that will enable, on the first hand,
an operator to aggregate, supervise and expose such massively
distributed resources and, on the other hand, developers to implement
new kinds of services that may be deployed and managed on demand is
still an open question.

%%  Delivierng en Edge IaaS system is complex
With their IOx and Fog Director software
solutions~\cite{bonomi2012fog}, Cisco allows IoT applications to run
on infrastructures composed of NFV-enabled hardware (at the edge) and
existing centralized clouds. However, their solution does not allow to
run Virtual Machines (VMs) and does not compete with existing IaaS
platforms.
%
The European Telecommunications Standards Institute (ETSI) MEC
Industry Specification Group defined in 2016 a software architecture
to orchestrate distinct independent cloud systems, \aka virtual
infrastructure managers in their terminology
(VIM)~\cite{7574435}. While the proposal should allow the deployment
of VMs at the edge, there is no implementation available yet.  At the
same time, a consortium composed of several industrial groups proposed
the ONAP framework~\cite{onap} that enables the orchestration and
automation of virtual network functions across distinct VIMs.  From
the academic side, brokering approaches have been also investigated.
For instance, the FogBow proposal~\cite{brasileiro2016fogbow} aims to
support large federations of Infrastructure-as-a-service (IaaS) cloud
providers. More recently, the NIST Cloud Computing Program (NCCP)
%Public Working Group has recognized the importance of advancement and development of
%frameworks to support seamless implementation of federated community
%cloud environments. In August 2017, the NCCP
%Public Working Group
% (PWG) on Federated Cloud (PWGFC)
initiated a collaborative effort with the IEEE P2302 group(, Standards for Intercloud Interoperability and
Federation (SIIF), to advance Federated Cloud) through the development
of a conceptual architecture and a vocabulary.
%The IEEE P2302 will
%develop a standard based on the NIST model.  Additional information
%can be found at
\footnote{\url{https://collaborate.nist.gov/twiki-cloud-computing/bin/view/CloudComputing/FederatedCloudPWGFC} (Valid on March 2018).}
%
While all these projects propose extensions to %current interfaces
% (APIs) to turn location into a first-class citizen, and
allow end-users/developers to manage edge application life cycle in geo-distributed
manner, they do not provide a well-suited software stack to enable
administrators to operate, and developers to use, edge infrastructures
like Cloud Computing ones.
%
Although Edge infrastructures significantly differ regarding heterogeneity, resiliency  and the potential
massive distribution of resources and networking environment,
administrators and end-users expect to find most features that makes
the success of the Cloud Computing paradigm.
%

In this paper, we propose two major contributions to favor the development of a resource management system for edge computing infrastructures~:
\begin{itemize}
\item A exhaustive list of the features that are expected from both administrators and end-users of edge computing infrastructures ; 
\item A discussion related to the pros and cons of possible design strategies (top/down and bottom up).
\end{itemize}

We highlight this study is done with any assumption but the fact that each edge site can communicate with the other ones eventually.

The remaining of the paper ...


% In this paper, we provide a list of expected features for both administrators and admins.
% We investigate whether a stack such as OpenStack, the defacto open-source standard can fullfil these requirements
% We finally discusss two possibles ways for moving forward: top/down vs bottom/up.

